
#Dr Peng example (note "#" means level 1 heading)
##Introduction  (note "##" means level 2 heading)
### echo=FALSE means code is not part of output document
####echo=FALSE means code is not part of output document
#####echo=FALSE means code is not part of output document
######echo=FALSE means code is not part of output document
###results="hide" means results of code chunk are not shown
```{r simulation,echo=FALSE}
set.seed(2)
x<-rnorm(100)
mean(x)
```

##Show how use code to insert in document

```{r determinetime,echo=FALSE}
time<-format(Sys.time(),"%a %b %d %X %Y")
rand<-rnorm(1)
```
The current time is `r time` and my favorite number is `r rand`.


#Making Tables

```{r tablename}
library(datasets)
data(airquality)
fit<-lm(Ozone~Wind + Temp + Solar.R, data = airquality)
```
Here is table of regression coefificeints.

```{r showtable,results="asis"}
library(xtable)
xt<-xtable(summary(fit))
print(xt, type="html")


#Global options can be set by running ```{r} opts_chunk$set(echo=FALSE,results=hide,fig.height=4,etc.)
###chache=TRUE as part of a codechunk will save the chunk's output and only run it if it is changed - a good option for long codes

